\TITLE

### 2021-01-28 final/vonLaszewski-covid-jds.tex
rename file anme with postfix final
fix WHO bibtex and shorten taitle for page header

\title[AICov: Deep
    Learning Framework for COVID-19 Forecasting with Population
    Covariates]{\TITLE}

@@

In summary, the AICov architecture allows the inclusion of new data
sources and models. An orchestrator enables modifying parameters and
selecting data sources and models used in the analysis. The framework
can be accessed via the interface layer that includes APIs, REST, and
Jupyter Notebooks. Compute interfaces are provided either by direct
access of GPUs from local resources or through the staging of
automatically generated REST services via our Cloudmesh REST Service
integrator
\citep{cloudmesh-openapi-install,cloudmesh-openapi-benchmark,cloudmesh-manual}.
Additionally, we can also access through abstractions cloud services
that are offered by the various cloud providers and are targeting our
application domain. Different models can be easily integrated into our
framework to verify our forecast or enhance our forecast based on the
users' models and data.

>>>>

\title[AICov: DL Framework for COVID-19 Forecasting with Population
    Covariates]{\TITLE}

@@

In summary, the AICov architecture allows the inclusion of new data
sources and models. An orchestrator enables modifying parameters and
selecting data sources and models used in the analysis. The framework
can be accessed via the interface layer that includes APIs, REST, and
Jupyter Notebooks. Compute interfaces are provided either by direct
access of GPUs from local resources or through the staging of
automatically generated REST services via our Cloudmesh REST Service
integrator
\citep{las-19-openapi-function,cloudmesh-openapi-install,cloudmesh-manual}.
Additionally, we can also access through abstractions cloud services
that are offered by the various cloud providers and are targeting our
application domain. Different models can be easily integrated into our
framework to verify our forecast or enhance our forecast based on the
users' models and data.
